Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-03 documentation/paper.tex
Defined gravitational differentiation function

>>>>

\subsection{Gravitational Differentiation}

Gravitational differentiation is a novel technique for gradient computation in the final layer of a neural network. It is intended for training a neural network in a semi-supervised fashion on a relatively small set of imperfectly labeled data, while simultaneously incorporating the network's changing predictions on a set of unlabeled data to encourage decisive classifications.

It makes use of the gravitational differentiation function $GravDiff(p, \psi, g)$, which is parameterized by the network's existing prediction $p$ on the training example in question, the degree $\psi$ of the piecewise exponential function used to distort the response of the gradient, and the gravitational multiplier $g$. The function is defined as follows:

$GravDiff(p, \psi, g) = g \cdot sgn(p) \cdot abs(tanh(2(p - 0.5))) ^ \psi$
